---
title: "flat_full.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
library(assertthat)
library(glue)
library(readr)
library(fusen)
library(dplyr)
library(stringr)

#data <- nyc_squirrels
path <- 'inst/nyc_squirrels_sample.csv'
file.exists(path)


assert_that(has_extension(path, 'csv'))
assert_that(is.dir(dirname(path)))
assert_that(is.readable(dirname(path)))
data <- read_csv(path)
assert_that(is.data.frame(data))
col <- "combination_of_primary_and_highlight_color"
assert_that(is.character(col))

data %>%
  select({{col}}) %>%
  

str_extract_all(data$combination_of_primary_and_highlight_color, pattern = "[A-Z,a-z]+", simplify = TRUE)


```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

# Include some data examples in your package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.
-->

```{r development-2}
# Run all this chunk in the console directly
# Create "inst/" directory
dir.create(here::here("inst"))

# Example dataset
file.copy(system.file("nyc_squirrels_sample.csv", package = "fusen"), here::here("inst"))
# Make your dataset file available to the current Rmd
pkgload::load_all(path = here::here(), export_all = FALSE)

# You will be able to read your example data file in each of your function examples and tests as follows
datafile <- system.file("nyc_squirrels_sample.csv", package = "autonomy")
nyc_squirrels <- read.csv(datafile)

nyc_squirrels
```


# The first function of the package: Calculate the median of a vector

<!--
Create a chunk for the core of the function

- The chunk needs to be named `function` at least
- It contains the code of a documented function
- The chunk can also be named `function-my_median` to make it easily
findable in your Rmd
- Let the `@examples` part empty, and use the next `examples` chunk instead

After inflating the template

-  This function code will be added in a new file in the "R/" directory
-->
# check_data_integrity function
This function allows the user to check the integrity of a provided dataset. First checks if the the extension of the filename is csv and the directory provided exists and is readable. Then it checks whether the dataset provided is a data frame and makes specific checks per column, as specified by the user.
```{r check_data_integrity}
#' check_data_integrity A function to check the integrity of a dataset, for the provided path, dataset class and included variables/columns.
#'
#' @param path a path where the file is stored, it includes the filename (type = character)
#' @param col a column name to make the checks on
#' @importFrom glue glue
#' @importFrom assertthat assert_that has_extension is.readable is.dir
#' @importFrom readr write_csv
#'
#' @return A message with an error if any of the conditions are not true, or with a confirmation that the checks for the column are successful.
#' @export
#'
#' @examples
check_data_integrity <- function(path = file.path('inst/nyc_squirrels_sample.csv'), col = "primary_fur_color") {
  file.exists(path)
  assert_that(has_extension(path, 'csv'))
  assert_that(is.dir(dirname(path)))
  assert_that(is.readable(dirname(path)))
  data <- read_csv(path)
  assert_that(is.data.frame(data))
  assert_that(is.character(col))
  
  
  
}
```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will be added in the '@examples' part of our function above in the "R/" directory
- This example will be added in the vignette created from this Rmd template
-->

```{r examples}
my_median(1:12)
```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will be added in the "tests/testthat/" directory
-->

```{r tests}
test_that("my_median works properly and show error if needed", {
  expect_true(my_median(1:12) == 6.5)
  expect_error(my_median("text"))
})
```

# Calculate the mean of a vector

<!--
There can be other functions, examples and tests in your flat template.
Each of them will be inflated in a different file, provided that there is a level-1 or level-2 section title to separate from previous functions.
-->

## Use sub-functions in the same chunk

```{r function-my_other_median}
#' My Other median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
my_other_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  sub_median(x, na.rm =na.rm)
}

#' Core of the median not exported
#' @param x Vector of Numeric values
#' @inheritParams stats::median
sub_median <- function(x, na.rm = TRUE) {
  stats::median(x, na.rm)
}
```

```{r examples-my_other_median}
my_other_median(1:12)
```

```{r tests-my_other_median}
test_that("my_median works properly and show error if needed", {
  expect_true(my_other_median(1:12) == 6.5)
  expect_error(my_other_median("text"))
})
```

<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Get started")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
